\titleformat Perfect Queries for Non-interactive\\Ulam Searching Game with Many Lies

### 2018-07-27 src/tex/buku/bab3.tex
kok udh 5 halaman aja sih

Kita tahu bahwa permasalahan Ulam dengan ruang pencarian $M$ dan maksimal bohong $e$ dapat deselesaikan dengan membuat $q$ query yang jika ditranspose akan membentuk kode biner $(n,M,d)_2$ dimana $d = 2*e+1$. Oleh karena itu tahap selanjutnya adalah jika diketahui $M$ dan $d$, bagaimana membuat seminimal mungkin $n$ agar kode biner $(n,M,d)_2$ valid. Langkah utama untuk membuat kode biner tersebut dengan $M$ dan $e$ yang diketahui adalah dengan menambahkan kode agar minimal jarak Hamming kode biner mencapai $e$.

>>>>

Kita tahu bahwa permasalahan Ulam dengan ruang pencarian $M$ dan maksimal bohong $e$ dapat deselesaikan dengan membuat $q$ query yang jika ditranspose akan membentuk kode biner $(n,M,d)_2$ dimana $d = 2*e+1$. Oleh karena itu tahap selanjutnya adalah jika diketahui $M$ dan $d$, bagaimana membuat seminimal mungkin $n$ agar kode biner $(n,M,d)_2$ valid. Langkah utama untuk membuat kode biner tersebut dengan $M$ dan $e$ yang diketahui adalah dengan menambahkan kode secara iteratif agar minimal jarak Hamming kode biner mencapai $e$.

### 2018-07-27 src/tex/paper-isst.tex
kok udh 5 halaman aja sih

Now again see a generator matrix $[7,3,4]_2$ in Figure \ref{fig:generator734} can create a perfect binary code $(7,8,4)_2$ code in Figure \ref{fig:binarycode784}. A generator matrix $[n, m, d]_2$ where $n = 2^m - 1$ and each \textbf{column} is a linear combination of $m$ bit binary string except $\vec{0}$ can make a perfect binary code $(n,M,d)_2$ where $d = M/2$.
\textbf{\textit{We need a profing or citation..}}

@@

Nah masalahnya, jika $d$ yang kita butuhkan kurang dari $M/2$, maka kita harus menggunakan seminimal mungkin $n$ kolom pertama $[M-1,M,M/2]_2$ sehingga menghasilkan $[n,M,d]_2$. Asumsikan kita memiliki fungsi $\aleph(d)$ adalah berapa kolom pada generator matrix yang akan menghasilkan kode biner dengan minimal jarak Hamming $d$. Hal yang pasti adalah $\aleph(M/2) = M-1$ dan $\aleph(1) = {log}_2(m)$ (need proving). Worst case adalah $\aleph(d)=M/2 + d - 1$. Best case adalah karena ada $M-1$ kolom untuk $0 \leq d \leq M/2$, maka $\aleph(d) = d/2$ (sepertinya tidak mungkin). Nah problem kita adalah bagaimana mengurutkan kolom pada generator matrix sehingga $\aleph(d)$ sesempurna mungkin, atau bisa dikatakan $\aleph(d) - \aleph(d-1) \approx 2$.

\noindent \textbf{Section Headings.} The section headings are in boldface capital and lowercase letters. 
Second level headings are typed as part of the succeeding paragraph (like the subsection heading of this paragraph).

\textbf{Figures}. Figures (refer with: Fig.~1, Fig.~2, ...) also should be presented as part of the text, leaving enough space so that the 
caption will not be confused with the text. The caption should be self-contained and placed \textit{below or beside }the 
figure. Generally, only original drawings or photographic reproductions are acceptable. Only very good photocopies are 
acceptable. Utmost care must be taken to \textit{insert the figures in correct alignment with the text}. Half-tone pictures
 should be in the form of glossy prints. If possible, please include your figures as graphic images in the electronic version. 
For best quality the pictures should have a resolution of 300 dpi(dots per inch).
\noindent Color figures are welcome for the online version of the journal. Generally, these figures will be reduced to black 
and white for the print version. The author should indicate on the checklist if he wishes to have them printed in full color 
and make the necessary payments in advance.

\vspace{6pt}
\textbf{Equations}.  Equations (refer with: Eq.~1, Eq.~2, ...) should be indented 5 mm (0.2"). 
There should be one line of space above the equation and one line of space below it before the text continues. 
The equations have to be numbered sequentially, and the number put in parentheses at the right-hand edge of the 
text. Equations should be punctuated as if they were an ordinary part of the text. Punctuation appears after the 
equation but before the equation number, e.g.

\begin{eqnarray}
c^2 = a^2 + b^2.
\end{eqnarray}

>>>>

Now again see a generator matrix $[7,3,4]_2$ in Figure \ref{fig:generator734} can create a perfect binary code $(7,8,4)_2$ code in Figure \ref{fig:binarycode784}. A generator matrix $[n, m, d]_2$ where $n = 2^m - 1$ and each \textbf{column} is all possible $m$ bits binary strings except $\vec{0}$ can make a perfect binary code $(n,M,d)_2$ where $d = M/2$.
\textbf{\textit{We need a proofing or citation..}}

@@

From a binary code, we can create a new binary code by modifying the existing binary code \cite{Huffman}. Modifications that can be done is to add and reduce the code. From a binary code $(n,M,d)_2 $, it can be deducted on a particular column so the binary code becomes $(n-1,M,d^\prime) _2 $ where $d^\prime = d$ or $d^\prime = d-1$. Similarly with the addition of code, from a binary code $(n,M,d)_2$, it can be added code so the binary code becomes $(n+1,M,d^\prime)_2 $ where $d^\prime = d$ or $d^\prime = d+1$.

We know that the Ulam problem with the $M$ search space and the maximum $e$ lies can be solved by making $q$ queries which if the set of the queries is transposed, it will form the binary code $(n,M,d) _2$ where $d=2*e+1$. Therefore the next stage is how to find as minimum as possible $n$ to make the binary code $(n,M,d)_2$ where $M$ and $d$ is known. The main step to make the binary code with $M$ and $e$ known is to add the code iteratively until its minimum Hamming distance reaches $e$.

Fig.~\ref{fig:hamming1} shows an illustration if $M = 8$, $n = 3$, and $d = 1$. The table in the picture shows the Hamming distance between codeword $x$ and $y$, so it can be concluded that the minimum Hamming distance is 1. Fig.~\ref{fig:hamming2} is addition of two codes from Fig.~\ref{fig:hamming1} so that $n = 5$ and $d = 2$.

\begin{figure}
\centering
\includegraphics[scale=0.7]{../img/hamming1.png}
\caption{Hasil tabel jarak Hamming pada $(3,8,1)_2$}
\label{fig:hamming1}
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.7]{../img/hamming2.png}
\caption{Hasil tabel jarak Hamming pada $(5,8,2)_2$}
\label{fig:hamming2}
\end{figure}
